### 2022-10-30 dissertation/chapters/06-bayesian-hyper-heuristic.tex
🚧 (chapter5): Conjugates review done

      \item $\theta \vert \alpha \sim Dir(\alpha; K)$: Denote the heuristic probability distribution, implementing a Dirchlet probability distribution parameterised by $\alpha$ and $K$. Heuristic selection probabilities are sampled from this distribution.
      \item $\phi \vert \beta \sim Dir(\beta; K)^{J}$: Denote the entity-heuristic probability distribution, implementing a Dirchlet probability distribution parameterised by $\beta$ and $K$ for each entity in the entity pool with population size $J$. Entity-heuristic probabilities are sampled from this distribution.
      \item $\psi \vert \gamma_{1}, \gamma_{0}  \sim Beta(\gamma_{1}, \gamma_{0})$: Denote the credit-heuristic probability distribution, implementing a Beta probability distribution parameterised by $\gamma_{1}$ and $\gamma_{0}$. Credit-heuristic probabilities are sampled from this distribution.

@@

The likelihood is presented in Equation~\eqref{eq:bhh:optimisation_step:map:bayesian_analysis_lamens} above. The event $H$ is a multinomial distribution with parameter $\theta$. It is known that the conjugate prior to a multinomial distribution is a Dirichlet distribution (see Chapter \ref{chap:probability}. The \textit{prior} probability distribution for  $\theta_{k}$ is thus presented in Equation~\eqref{eq:bhh:optimisation_step:map:map_theta_prior} below.

@@

Finally, the event $C$ is a binomial distribution with parameter $\psi$. It is known that the conjugate prior to a binomial distribution is a Beta distribution (see Chapter \ref{chap:probability}). The prior probability distribution for $\psi_{k}$ is thus presented in Equation~\eqref{eq:bhh:optimisation_step:map:map_psi_prior} below.

@@

Normalisation is a hyper-parameter that aims to provide a mechanism of control for the degree to which exploration is allowed. Figure \ref{sec:bhh:hyper_parameters:discounted_rewards:normalisation} shows the effect of different concentrations ($\alpha$ and $\beta$) on the Beta distribution. By normalising the concentration parameters for the \ac{BHH} ($\alpha$, $\beta$, $\gamma_{1}$ and $\gamma_{0}$), the variance of the selection probability distributions increase, allowing for sampled probabilities further from the mean and thus allowing for more exploration.

\begin{figure}[htbp]
      \begin{subfigure}{0.5\textwidth}
            \includegraphics[width=\textwidth]{images/beta_1_1.png}
            \caption{$\alpha=1$, $\beta=1$}
            \label{sec:bhh:hyper_parameters:normalisation_beta_1_1}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \includegraphics[width=\textwidth]{images/beta_5_5.png}
            \caption{$\alpha=5$, $\beta=5$}
            \label{sec:bhh:hyper_parameters:normalisation_beta_5_5}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/beta_20_20.png}
            \caption{$\alpha=20$, $\beta=20$}
            \label{sec:bhh:hyper_parameters:normalisation_beta_20_20}
      \end{subfigure}
      \par\bigskip
      \caption{Beta distribution with varying $\alpha$ and $\beta$ values.}
      \label{sec:bhh:hyper_parameters:discounted_rewards:normalisation}
\end{figure}

>>>>

      \item $\theta \vert \alpha \sim Dir(\alpha; K)$: Denote the heuristic probability distribution, implementing a Dirichlet probability distribution parameterised by $\alpha$ and $K$. Heuristic selection probabilities are sampled from this distribution.
      \item $\phi \vert \beta \sim Dir(\beta; K)^{J}$: Denote the entity-heuristic probability distribution, implementing a Dirichlet probability distribution parameterised by $\beta$ and $K$ for each entity in the entity pool with population size $J$. Entity-heuristic probabilities are sampled from this distribution.
      \item $\psi \vert \gamma_{1}, \gamma_{0}  \sim Beta(\gamma_{1}, \gamma_{0})$: Denote the credit-heuristic probability distribution, implementing a Beta probability distribution parameterised by $\gamma_{1}$ and $\gamma_{0}$. Credit-heuristic probabilities are sampled from this distribution.

@@

The likelihood is presented in Equation~\eqref{eq:bhh:optimisation_step:map:bayesian_analysis_lamens} above. The event $H$ is a multinomial distribution with parameter $\theta$. It is known that the conjugate prior to a multinomial distribution is a Dirichlet probability distribution (see Chapter \ref{chap:probability}. The \textit{prior} probability distribution for  $\theta_{k}$ is thus presented in Equation~\eqref{eq:bhh:optimisation_step:map:map_theta_prior} below.

@@

Finally, the event $C$ is a binomial distribution with parameter $\psi$. It is known that the conjugate prior to a binomial distribution is a Beta probability distribution (see Chapter \ref{chap:probability}). The prior probability distribution for $\psi_{k}$ is thus presented in Equation~\eqref{eq:bhh:optimisation_step:map:map_psi_prior} below.

@@

Normalisation is a hyper-parameter that aims to provide a mechanism of control for the degree to which exploration is allowed. Figure \ref{sec:bhh:hyper_parameters:discounted_rewards:normalisation} shows the effect of different concentrations ($\alpha$ and $\beta$) on the Beta probability distribution. By normalising the concentration parameters for the \ac{BHH} ($\alpha$, $\beta$, $\gamma_{1}$ and $\gamma_{0}$), the variance of the selection probability distributions increase, allowing for sampled probabilities further from the mean and thus allowing for more exploration.

\begin{figure}[htbp]
      \begin{subfigure}{0.5\textwidth}
            \includegraphics[width=\textwidth]{images/beta_1_1.png}
            \caption{$\alpha=1$, $\beta=1$}
            \label{sec:bhh:hyper_parameters:normalisation_beta_1_1}
      \end{subfigure}
      \begin{subfigure}{0.5\textwidth}
            \includegraphics[width=\textwidth]{images/beta_5_5.png}
            \caption{$\alpha=5$, $\beta=5$}
            \label{sec:bhh:hyper_parameters:normalisation_beta_5_5}
      \end{subfigure}
      \par\bigskip
      \begin{subfigure}{0.5\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/beta_20_20.png}
            \caption{$\alpha=20$, $\beta=20$}
            \label{sec:bhh:hyper_parameters:normalisation_beta_20_20}
      \end{subfigure}
      \par\bigskip
      \caption{Beta probability distribution with varying $\alpha$ and $\beta$ values.}
      \label{sec:bhh:hyper_parameters:discounted_rewards:normalisation}
\end{figure}

### 2022-10-30 dissertation/chapters/09-conclusion.tex
🚧 WIP - Save point (compiles)
🚧 (chapter5): Conjugates review done

Investigation was done into the landscapes of existing solutions to train \acp{FFNN} as well as \acp{HH}. Though there exists many applications of \acp{HH} there are little to no published work on using \acp{HH} to train \acp{FFNN}. The only work that was found include the work by \citeauthor{ref:nel:2021} \cite{ref:nel:2021}.

@@

Credit assignment in the context of this dissertation was has 2 outcomes, true and false. Therefore, credit assignment and by definition performance evaluation is modeled as a \index{binomial distribution} distribution with a \index{beta probability distribution}beta probability distribution as a prior probability distribution. Heuristic selection has multiple possible outcomes, yielding a index associated with a heuristic. Therefore, heuristic selection is modeled as a \index{multionomial}multinomial/\index{categorical}categorical with a dirichlet probability distribution as a prior probability distribution. Since the dirichlet-multinomial distributions are the multivariate extensions of the beta-binomial distributions, it show be possible to extend credit assignment to a multivariate version. A suggestion then is to learn which credit assignment to select. The results of this have show that credit assignment is problem-dependent. Therefore, include credit selection as part of the selection pool implemented by the \ac{BHH}. One could then include multiple strategies, each with varying exploration-exploitation trade-off.

>>>>

Investigation was done into the landscapes of existing solutions to train \acp{FFNN} as well as \acp{HH}. Though there exists many applications of \acp{HH} there are little to no published work on using \acp{HH} to train \acp{FFNN}. The only work that was found include the work by~\citeauthor{ref:nel:2021}~\cite{ref:nel:2021}.

@@

Credit assignment in the context of this dissertation was has 2 outcomes, true and false. Therefore, credit assignment and by definition performance evaluation is modeled as a \index{binomial distribution} distribution with a \index{Beta probability distribution}Beta probability distribution as a prior probability distribution. Heuristic selection has multiple possible outcomes, yielding a index associated with a heuristic. Therefore, heuristic selection is modeled as a \index{multionomial}multinomial/\index{categorical}categorical with a dirichlet probability distribution as a prior probability distribution. Since the dirichlet-multinomial distributions are the multivariate extensions of the beta-binomial distributions, it show be possible to extend credit assignment to a multivariate version. A suggestion then is to learn which credit assignment to select. The results of this have show that credit assignment is problem-dependent. Therefore, include credit selection as part of the selection pool implemented by the \ac{BHH}. One could then include multiple strategies, each with varying exploration-exploitation trade-off.
